\Rpackage{MSnbase} development

### 2011-05-06 inst/doc/Foreword.tex
added incomplete dissociation and spectral counting sections to demo vignette and mention bio-sig-proteomics list
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@55300 bc3139a8-67e5-0310-9ffc-ced21a209358

>>>>

\bigskip

You are wellcome to contact me for questions, bugs, typos or suggestions about \Rpackage{MSnbase}. 
If you wish to reach a broader audience for general questions about proteomics analysis using \texttt{R}, 
you may want to use the Bioconductor proteomics special interest 
group\footnote{\url{https://stat.ethz.ch/mailman/listinfo/bioc-sig-proteomics}}.
